quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-09 paper-quollr.Rmd
Fixed Figure 12 and 13

nldr_plt <- shared_df |>
  ggplot(aes(x = emb1, y = emb2, colour = cluster)) +
  geom_point(alpha=0.5, size = 0.8) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 0.5) +
  scale_color_manual(values = c("0" = '#66c2a5',"1" = '#fc8d62',"2" = '#8da0cb',"3" = '#e78ac3',"4" = '#a6d854',"5" = '#ffd92f',"6" = '#e5c494')) +
  theme_linedraw() +
  theme(
    #aspect.ratio = 1,
    plot.background = element_rect(fill = 'transparent', colour = NA),
    plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
    panel.background = element_rect(fill = 'transparent',
                                    colour = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(), axis.title.y = element_blank(),
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank(),
    legend.position = "none"
  )

nldr_plt <- ggplotly(nldr_plt, width = 250,
                     height = 250, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "350px", height = "250px")

linked_plt_int <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: center;
    justify-items: center;
    margin: 0;
    padding: 0;",
        nldr_plt, 
        htmltools::div(style = "margin-top: 30px;", langevitour_output)
    ),
    device = "xs"
)

@@

nldr_plt <- shared_df |>
  ggplot(aes(x = emb1, y = emb2, colour = cluster)) +
  geom_point(alpha=0.5, size = 0.8) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 0.5) +
  scale_color_manual(values = c("0" = '#66c2a5',"1" = '#fc8d62',"2" = '#8da0cb',"3" = '#e78ac3',"4" = '#a6d854',"5" = '#ffd92f',"6" = '#e5c494')) +
  theme_linedraw() +
  theme(
    #aspect.ratio = 1,
    plot.background = element_rect(fill = 'transparent', colour = NA),
    plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
    panel.background = element_rect(fill = 'transparent',
                                    colour = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(), axis.title.y = element_blank(),
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank(),
    legend.position = "none"
  )

nldr_plt <- ggplotly(nldr_plt, width = 250,
                     height = 250, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "350px", height = "250px")

linked_plt_best <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: center;
    justify-items: center;
    margin: 0;
    padding: 0;",
        nldr_plt, 
        htmltools::div(style = "margin-top: 20px;", langevitour_output)
    ),
    device = "xs"
)
```

>>>>

cluster_colors <- c(
    "0" = '#66c2a5', "1" = '#fc8d62', "2" = '#8da0cb',
    "3" = '#e78ac3', "4" = '#a6d854', "5" = '#ffd92f', "6" = '#e5c494'
)

# Scatter points
nldr_plt <- plot_ly(
    data = shared_df,
    x = ~emb1, y = ~emb2,
    type = "scatter", mode = "markers",
    color = ~cluster, colors = cluster_colors,
    marker = list(size = 3, opacity = 0.5),
    hoverinfo = "skip",  # <-- skip hover completely
    showlegend = FALSE
)

# Add line segments
if (nrow(trimesh_data_limb) > 0) {
    nldr_plt <- nldr_plt |>
        add_segments(
            data = trimesh_data_limb,
            x = ~x_from, y = ~y_from,
            xend = ~x_to, yend = ~y_to,
            line = list(color = "#000000", width = 0.5),
            inherit = FALSE,
            showlegend = FALSE,
            hoverinfo = "skip"  # <-- skip hover
        )
}

# Layout: axes, border, no tooltip
nldr_plt <- nldr_plt |>
    layout(
        width = 310, height = 310,
        margin = list(l = 20, r = 20, t = 20, b = 20),
        xaxis = list(title = "", showgrid = FALSE, zeroline = FALSE,
                     showticklabels = FALSE, ticks = "", linecolor = "black", mirror = TRUE),
        yaxis = list(title = "", showgrid = FALSE, zeroline = FALSE,
                     showticklabels = FALSE, ticks = "", linecolor = "black", mirror = TRUE)
    ) |>
    style(
        selected = list(marker = list(opacity = 1)),
        unselected = list(marker = list(opacity = 1))
    ) |>
    highlight(
        on = "plotly_selected",
        off = "plotly_deselect"
    ) |>
    config(displayModeBar = FALSE)

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "370px", height = "370px")

linked_plt_int <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 380px;
    width: 500px",
        nldr_plt, 
        htmltools::div(style = "margin-top: 20px;", langevitour_output)
    ),
    device = "xs"
)

@@

cluster_colors <- c(
    "0" = '#66c2a5', "1" = '#fc8d62', "2" = '#8da0cb',
    "3" = '#e78ac3', "4" = '#a6d854', "5" = '#ffd92f', "6" = '#e5c494'
)

# Scatter points
nldr_plt <- plot_ly(
    data = shared_df,
    x = ~emb1, y = ~emb2,
    type = "scatter", mode = "markers",
    color = ~cluster, colors = cluster_colors,
    marker = list(size = 3, opacity = 0.5),
    hoverinfo = "skip",  # <-- skip hover completely
    showlegend = FALSE
)

# Add line segments
if (nrow(trimesh_data_limb) > 0) {
    nldr_plt <- nldr_plt |>
        add_segments(
            data = trimesh_data_limb,
            x = ~x_from, y = ~y_from,
            xend = ~x_to, yend = ~y_to,
            line = list(color = "#000000", width = 0.5),
            inherit = FALSE,
            showlegend = FALSE,
            hoverinfo = "skip"  # <-- skip hover
        )
}

# Layout: axes, border, no tooltip
nldr_plt <- nldr_plt |>
    layout(
        width = 310, height = 310,
        margin = list(l = 20, r = 20, t = 20, b = 20),
        xaxis = list(title = "", showgrid = FALSE, zeroline = FALSE,
                     showticklabels = FALSE, ticks = "", linecolor = "black", mirror = TRUE),
        yaxis = list(title = "", showgrid = FALSE, zeroline = FALSE,
                     showticklabels = FALSE, ticks = "", linecolor = "black", mirror = TRUE)
    ) |>
    style(
        selected = list(marker = list(opacity = 1)),
        unselected = list(marker = list(opacity = 1))
    ) |>
    highlight(
        on = "plotly_selected",
        off = "plotly_deselect"
    ) |>
    config(displayModeBar = FALSE)

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "370px", height = "370px")

linked_plt_best <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 380px;
    width: 500px",
        nldr_plt, 
        htmltools::div(style = "margin-top: 20px;", langevitour_output)
    ),
    device = "xs"
)
```
